---
title: "TMT Over and Underlabeling Analysis"
output: html_document
date: "2024-01-28"
---

## Overlabeling Analysis - VARIABLE LYS/N-TERM MOD

## Import fragpipe ion level data
## There are 8 relevant fragpipe outputs: These are two different search criteria (allowing or omitting overlabelling) for each of the 4 samples (Brain Bound, Brain Unbound, MLE12 Bound, MLE12 Unbound)

## This method is different from Carr MCP Paper - here Lys modification is variable and this seems to result in many non-amino TMT assignments - in other words fragpipe appears to assign many N-terminal modifications to the first few side chains, but unlikely the fragmentation data would support these assignments

```{r}

library(readr)
ion_brain_bound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_brain_bound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_brain_unbound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_brain_unbound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_bound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_MLE_bound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_unbound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_MLE_unbound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_brain_bound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/ion_brain_bound_overlabeling_allowed.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_brain_unbound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/ion_brain_unbound_overlabeling_allowed.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_bound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/ion_MLE_bound_overlabeling_allowed.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_unbound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/ion_MLE_unbound_overlabeling_allowed.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

```



## Define a function to determine percentage of overlabelled precursors
# Here the denominator is rows, meaning this asks what percentage of precursor ions have these non-amino TMT acylations
```{r}

overlabelling <- function(df) {
  # Capture the name of the input dataframe
  df_name <- deparse(substitute(df))

  # Remove rows with 'contam' in the beginning of the 'Protein' column
  df <- df[!grepl("^contam", df$Protein), ]

  # Function to calculate percentage of overlabelled precursors
  calculate_percentage <- function(sub_df, letter) {
    count <- sum(grepl(paste0(letter, "\\(304.2071\\)"), sub_df$`Assigned Modifications`), na.rm = TRUE)
    return(100 * count / nrow(sub_df))
  }

  # Calculate percentages for Y, S, T, and H
  for (letter in c("Y", "S", "T", "H")) {
    percentage <- calculate_percentage(df, letter)
    assign(paste0(df_name, "_overlabelled_percentage_", letter), percentage, envir = .GlobalEnv)
  }

  # Return the modified dataframe
  df
}


```


## Apply the overlabeling function
## Visualize
```{r}

ion_brain_bound_overlabeling_allowed <- overlabelling(ion_brain_bound_overlabeling_allowed)
ion_brain_unbound_overlabeling_allowed <- overlabelling(ion_brain_unbound_overlabeling_allowed)
ion_MLE_bound_overlabeling_allowed <- overlabelling(ion_MLE_bound_overlabeling_allowed)
ion_MLE_unbound_overlabeling_allowed <- overlabelling(ion_MLE_unbound_overlabeling_allowed)

## Visualize the overlabelling

# Manually creating a dataframe with the overlabelled percentage values
data_to_plot <- data.frame(
  Dataset = rep(c("brain_bound", "brain_unbound", "MLE_bound", "MLE_unbound"), each = 4),
  Modification = rep(c("Ser", "Tyr", "Thr", "His"), 4),
  Percentage = c(
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_H
  )
)

# Creating the bar plot
ggplot(data_to_plot, aes(x = interaction(Dataset, Modification), y = Percentage, fill = Modification)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme_minimal() +
  labs(title = "Overlabelling Percentage for Different Modifications\nPer Precursor Ion", x = "Dataset and Modification", y = "Percentage Overlabelled (%)") +
  scale_y_continuous(limits = c(0, 50)) +
  scale_fill_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Adjust x-axis labels angle


```



## Define a function to determine percentage of overlabelled precursors
# Here the denominator is not precursor ions but rather total number of the given amino acids
# This answers the questions of "what percentage of all Tyr are TMT labelled, same for Ser, Thr, His
```{r}

overlabelling <- function(df) {
  # Capture the name of the input dataframe
  df_name <- deparse(substitute(df))

  # Remove rows with 'contam' in the beginning of the 'Protein' column
  df <- df[!grepl("^contam", df$Protein), ]

  # Function to calculate the total count of a specific amino acid in all peptide sequences
  total_amino_acid_count <- function(sub_df, letter) {
    sum(sapply(sub_df$`Peptide Sequence`, function(peptide) sum(strsplit(peptide, "")[[1]] == letter)), na.rm = TRUE)
  }

  # Function to calculate percentage of overlabelled precursors based on the amino acid count
  calculate_percentage <- function(sub_df, letter) {
    # Count how many times the specific mass tag is found in association with the amino acid
    overlabelled_count <- sum(grepl(paste0(letter, "\\(304.2071\\)"), sub_df$`Assigned Modifications`), na.rm = TRUE)
    # Get the total count of the amino acid in all peptide sequences
    amino_acid_total_count <- total_amino_acid_count(sub_df, letter)
    # Calculate the percentage
    if (amino_acid_total_count > 0) {
      return(100 * overlabelled_count / amino_acid_total_count)
    } else {
      return(NA)  # Return NA if the amino acid is not found in any peptide sequences
    }
  }

  # Calculate percentages for Y, S, T, and H
  for (letter in c("Y", "S", "T", "H")) {
    percentage <- calculate_percentage(df, letter)
    assign(paste0(df_name, "_overlabelled_percentage_", letter), percentage, envir = .GlobalEnv)
  }

  # Return the modified dataframe
  return(df)
}

```



## Apply the overlabeling function
## Visualize
```{r}

ion_brain_bound_overlabeling_allowed <- overlabelling(ion_brain_bound_overlabeling_allowed)
ion_brain_unbound_overlabeling_allowed <- overlabelling(ion_brain_unbound_overlabeling_allowed)
ion_MLE_bound_overlabeling_allowed <- overlabelling(ion_MLE_bound_overlabeling_allowed)
ion_MLE_unbound_overlabeling_allowed <- overlabelling(ion_MLE_unbound_overlabeling_allowed)

## Visualize the overlabelling

# Manually creating a dataframe with the overlabelled percentage values
data_to_plot <- data.frame(
  Dataset = rep(c("brain_bound", "brain_unbound", "MLE_bound", "MLE_unbound"), each = 4),
  Modification = rep(c("Ser", "Tyr", "Thr", "His"), 4),
  Percentage = c(
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_H
  )
)

# Creating the bar plot
ggplot(data_to_plot, aes(x = interaction(Dataset, Modification), y = Percentage, fill = Modification)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme_minimal() +
  labs(title = "Overlabelling Percentage for Different Modifications\nPer Amino Acid", x = "Dataset and Modification", y = "Percentage Overlabelled (%)") +
  scale_y_continuous(limits = c(0, 50)) +
  scale_fill_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Adjust x-axis labels angle


```




### Overlabelling - FIXED LYS/AMINO MOD
### Search performed with fixed amino modifications similar to Carr MCP paper (TMT for the Masses)

## Import fragpipe ion level data
## There are 8 relevant fragpipe outputs: These are two different search criteria (allowing or omitting overlabelling) for each of the 4 samples (Brain Bound, Brain Unbound, MLE12 Bound, MLE12 Unbound)

```{r}

library(readr)

ion_brain_bound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/for_R_exp18_overlabelled_allowed_amines_fixed/brain_bound_ion.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_brain_unbound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/for_R_exp18_overlabelled_allowed_amines_fixed/brain_unbound_ion.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_bound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/for_R_exp18_overlabelled_allowed_amines_fixed/MLE_bound_ion.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_unbound_overlabeling_allowed <- read_delim("fragpipe_ion_outputs/for_R_exp18_overlabelled_allowed_amines_fixed/MLE_unbound_ion.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

```



## Define a function to determine percentage of overlabelled precursors
# Here the denominator is rows, meaning this asks what percentage of precursor ions have these non-amino TMT acylations
```{r}

overlabelling <- function(df) {
  # Capture the name of the input dataframe
  df_name <- deparse(substitute(df))

  # Remove rows with 'contam' in the beginning of the 'Protein' column
  df <- df[!grepl("^contam", df$Protein), ]

  # Function to calculate percentage of overlabelled precursors
  calculate_percentage <- function(sub_df, letter) {
    count <- sum(grepl(paste0(letter, "\\(304.2071\\)"), sub_df$`Assigned Modifications`), na.rm = TRUE)
    return(100 * count / nrow(sub_df))
  }

  # Calculate percentages for Y, S, T, and H
  for (letter in c("Y", "S", "T", "H")) {
    percentage <- calculate_percentage(df, letter)
    assign(paste0(df_name, "_overlabelled_percentage_", letter), percentage, envir = .GlobalEnv)
  }

  # Return the modified dataframe
  df
}


```


## Define a my_theme
```{r}

library(ggplot2)

my_barplot_theme <- function() {
  theme_minimal() +
    theme(
      plot.title = element_text(size = 18),            # Title font size
      axis.title.x = element_text(size = 14),          # X-axis title font size
      axis.title.y = element_text(size = 20),          # Y-axis title font size
      axis.text.x = element_text(size = 14),           # X-axis labels font size
      axis.text.y = element_text(size = 20)            # Y-axis labels font size
    )
}

```





## Apply the overlabeling function
## Visualize
```{r}

ion_brain_bound_overlabeling_allowed <- overlabelling(ion_brain_bound_overlabeling_allowed)
ion_brain_unbound_overlabeling_allowed <- overlabelling(ion_brain_unbound_overlabeling_allowed)
ion_MLE_bound_overlabeling_allowed <- overlabelling(ion_MLE_bound_overlabeling_allowed)
ion_MLE_unbound_overlabeling_allowed <- overlabelling(ion_MLE_unbound_overlabeling_allowed)

## Visualize the overlabelling

# Manually creating a dataframe with the overlabelled percentage values
data_to_plot <- data.frame(
  Dataset = rep(c("brain_bound", "brain_unbound", "MLE_bound", "MLE_unbound"), each = 4),
  Modification = rep(c("Ser", "Tyr", "Thr", "His"), 4),
  Percentage = c(
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_H
  )
)

# Creating the bar plot
ggplot(data_to_plot, aes(x = Dataset, y = Percentage, fill = Modification)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)), # Format the label to one decimal place
            position = position_dodge(width = 0.9),    # Align text in the center of the bars
            vjust = -0.5,                              # Adjust vertical position to be above the bar
            size = 3) +                                # Adjust text size, if needed
  theme_minimal() +
  labs(title = "TMT Overlabelling: On-Quartz vs Solution Phase",
       x = "",
       y = "Overlabelled Precursors (%)",
       fill = "Amino Acid") +
  scale_y_continuous(limits = c(0, 30)) +
  scale_fill_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # Adjust x-axis labels angle
  my_barplot_theme()
  
```



## Define a function to determine percentage of overlabelled precursors
# Here the denominator is not precursor ions but rather total number of the given amino acids
# This answers the questions of "what percentage of all Tyr are TMT labelled, same for Ser, Thr, His
```{r}

overlabelling <- function(df) {
  # Capture the name of the input dataframe
  df_name <- deparse(substitute(df))

  # Remove rows with 'contam' in the beginning of the 'Protein' column
  df <- df[!grepl("^contam", df$Protein), ]

  # Function to calculate the total count of a specific amino acid in all peptide sequences
  total_amino_acid_count <- function(sub_df, letter) {
    sum(sapply(sub_df$`Peptide Sequence`, function(peptide) sum(strsplit(peptide, "")[[1]] == letter)), na.rm = TRUE)
  }

  # Function to calculate percentage of overlabelled precursors based on the amino acid count
  calculate_percentage <- function(sub_df, letter) {
    # Count how many times the specific mass tag is found in association with the amino acid
    overlabelled_count <- sum(grepl(paste0(letter, "\\(304.2071\\)"), sub_df$`Assigned Modifications`), na.rm = TRUE)
    # Get the total count of the amino acid in all peptide sequences
    amino_acid_total_count <- total_amino_acid_count(sub_df, letter)
    # Calculate the percentage
    if (amino_acid_total_count > 0) {
      return(100 * overlabelled_count / amino_acid_total_count)
    } else {
      return(NA)  # Return NA if the amino acid is not found in any peptide sequences
    }
  }

  # Calculate percentages for Y, S, T, and H
  for (letter in c("Y", "S", "T", "H")) {
    percentage <- calculate_percentage(df, letter)
    assign(paste0(df_name, "_overlabelled_percentage_", letter), percentage, envir = .GlobalEnv)
  }

  # Return the modified dataframe
  return(df)
}

```



## Apply the overlabeling function
## Visualize
```{r}

ion_brain_bound_overlabeling_allowed <- overlabelling(ion_brain_bound_overlabeling_allowed)
ion_brain_unbound_overlabeling_allowed <- overlabelling(ion_brain_unbound_overlabeling_allowed)
ion_MLE_bound_overlabeling_allowed <- overlabelling(ion_MLE_bound_overlabeling_allowed)
ion_MLE_unbound_overlabeling_allowed <- overlabelling(ion_MLE_unbound_overlabeling_allowed)

## Visualize the overlabelling

# Manually creating a dataframe with the overlabelled percentage values
data_to_plot <- data.frame(
  Dataset = rep(c("brain_bound", "brain_unbound", "MLE_bound", "MLE_unbound"), each = 4),
  Modification = rep(c("Ser", "Tyr", "Thr", "His"), 4),
  Percentage = c(
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_brain_unbound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_bound_overlabeling_allowed_overlabelled_percentage_H,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_S,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_Y,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_T,
    ion_MLE_unbound_overlabeling_allowed_overlabelled_percentage_H
  )
)

# Creating the bar plot
ggplot(data_to_plot, aes(x = interaction(Dataset, Modification), y = Percentage, fill = Modification)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  theme_minimal() +
  labs(title = "Overlabelling Percentage for Different Modifications\nPer Amino Acid", x = "Dataset and Modification", y = "Percentage Overlabelled (%)") +
  scale_y_continuous(limits = c(0, 50)) +
  scale_fill_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Adjust x-axis labels angle


```

