---
title: "TMT Over and Underlabeling Analysis"
output: html_document
date: "2024-01-28"
---

## Underlabeling Analysis

## Import fragpipe ion level data
## There are 4 relevant fragpipe outputs (one for each sample: Brain Bound, Brain Unbound, MLE12 Bound, MLE12 Unbound)
## Using the searches with overlabeling omitted (allows for labeling only on N-term and Lys)
```{r}

library(readr)
ion_brain_bound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_brain_bound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_brain_unbound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_brain_unbound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_bound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_MLE_bound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

ion_MLE_unbound_overlabeling_omitted <- read_delim("fragpipe_ion_outputs/ion_MLE_unbound_overlabeling_omitted.tsv", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

```



## Define a function to assess underlabeling
# # Underlabeling is defined as a precursor ion that completely lacks a TMT.
# To achieve this task, we will define a function in R that performs the following steps:
# 1) Remove Rows with "contam" in Protein Column: The function will filter out rows where the Protein column starts with the string "contam".
# 2) Keep only rows that have a Cysteine
# 3) Analyze "Assigned Modifications" Column: Add a new column Underlabelled initialized to No. For each row, if the Assigned Modifications column does not contain the string "304.2071", then write Yes in this column.
# 4) Determine if the ion has a K (Lys) or not.
```{r}

underlabeling <- function(df) {
  # Capture the name of the input dataframe
  df_name <- deparse(substitute(df))

  # Remove rows with 'contam' in the beginning of the 'Protein' column
  df <- df[!grepl("^contam", df$Protein), ]

  # Initialize 'Underlabelled_precursor' column to 'No'
  df$Underlabelled_precursor <- 'No'

  # Initialize 'Lys_containing' column to 'No'
  df$Lys_containing <- 'No'

  # Update 'Underlabelled_precursor' to 'Yes' where 'Assigned Modifications' does not contain '304.2071'
  df$Underlabelled_precursor <- ifelse(grepl("304.2071", df$`Assigned Modifications`), 'No', 'Yes')

  # Update 'Lys_containing' to 'Yes' where 'Peptide Sequence' contains 'K'
  df$Lys_containing <- ifelse(grepl("K", df$`Peptide Sequence`), 'Yes', 'No')


 # Function to calculate the percentage of underlabelled_precursor
  calculate_percentage <- function(sub_df) {
    if (nrow(sub_df) == 0) {
      return(NA)  # Return NA if the subset dataframe has no rows
    }
    return(100 * sum(sub_df$Underlabelled_precursor == "Yes", na.rm = TRUE) / nrow(sub_df))
  }

  # Filter for Lys_containing = Yes and calculate percentage
  df_lys_yes <- subset(df, Lys_containing == "Yes")
  percentage_lys_yes <- calculate_percentage(df_lys_yes)
  assign(paste0(df_name, "_underlabelled_percentage_K_yes"), percentage_lys_yes, envir = .GlobalEnv)

  # Filter for Lys_containing = No and calculate percentage
  df_lys_no <- subset(df, Lys_containing == "No")
  percentage_lys_no <- calculate_percentage(df_lys_no)
  assign(paste0(df_name, "_underlabelled_percentage_K_no"), percentage_lys_no, envir = .GlobalEnv)

  # Return the modified dataframe
  df
}


```

## Apply the underlabeling function to each sample
```{r}

ion_brain_bound_overlabeling_omitted <- underlabeling(ion_brain_bound_overlabeling_omitted)
ion_brain_unbound_overlabeling_omitted <- underlabeling(ion_brain_unbound_overlabeling_omitted)
ion_MLE_bound_overlabeling_omitted <- underlabeling(ion_MLE_bound_overlabeling_omitted)
ion_MLE_unbound_overlabeling_omitted <- underlabeling(ion_MLE_unbound_overlabeling_omitted)

```



## Define a mytheme

```{r}

library(ggplot2)

my_barplot_theme <- function() {
  theme_minimal() +
    theme(
      plot.title = element_text(size = 18),            # Title font size
      axis.title.x = element_text(size = 14),          # X-axis title font size
      axis.title.y = element_text(size = 20),          # Y-axis title font size
      axis.text.x = element_text(size = 14),           # X-axis labels font size
      axis.text.y = element_text(size = 20)            # Y-axis labels font size
    )
}

```


# Visualization of underlabelled Cys-containing precursor ions
```{r}

library(ggplot2)

# Manually creating a dataframe with the percentage values and shorter dataset names
data_to_plot <- data.frame(
  Dataset = rep(c("brain_bound", "brain_unbound", "MLE_bound", "MLE_unbound"), each = 2),
  Category = rep(c("K_yes", "K_no"), 4),
  Percentage = c(
    ion_brain_bound_overlabeling_omitted_underlabelled_percentage_K_yes,
    ion_brain_bound_overlabeling_omitted_underlabelled_percentage_K_no,
    ion_brain_unbound_overlabeling_omitted_underlabelled_percentage_K_yes,
    ion_brain_unbound_overlabeling_omitted_underlabelled_percentage_K_no,
    ion_MLE_bound_overlabeling_omitted_underlabelled_percentage_K_yes,
    ion_MLE_bound_overlabeling_omitted_underlabelled_percentage_K_no,
    ion_MLE_unbound_overlabeling_omitted_underlabelled_percentage_K_yes,
    ion_MLE_unbound_overlabeling_omitted_underlabelled_percentage_K_no
  )
)

# Creating the bar plot
# Assuming the rest of your code is unchanged and my_barplot_theme is already defined appropriately
underlabeling_plot <- ggplot(data_to_plot, aes(x = Dataset, y = Percentage, fill = Category)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.75)) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage), 
                y = Percentage + 2,  # Adjust the y position slightly above the bar
                group = Category),
            position = position_dodge(width = 0.75),
            vjust = 0,  # Vertically adjust to position above the bar
            size = 3.5) +  # Adjust text size as needed
  labs(title = "TMT Underlabeling: On-Quartz vs. Solution Phase", x = "", y = "Underlabelled Precursors (%)") +
  scale_y_continuous(limits = c(0, 50)) +
  scale_fill_manual(values = c("K_yes" = "blue", "K_no" = "red")) +
  my_barplot_theme(
  )

print(underlabeling_plot)

# Save the plot as a PDF
ggsave("underlabeling_plot.pdf", plot = underlabeling_plot, width = 8, height = 6)


```


